working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
More edits

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

@@

Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2. Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial. Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases. *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of no production of fruit in apomictic treatments.

>>>>

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The species selected (**Table 1**) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

@@

Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in **Table 2**. Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine. The 100% foreign pollen treatments barely produced seeds or fruits and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial. Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases. *S. lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size. *C. annuum* produced some fruits (9%) of both small and normal size and finally *S. melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with apomictic treatments.

### 2018-12-11 Manuscript_draft/Manuscript_draft.tex
More edits

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The species selected (Table 1)
belonged to three different families, Solanaceae, Brassicaceae and
Convolvulaceae. The criteria of species/family selection was based on
close/distant related species (see phylogenetic tree for relatedness fig
1), heterogeneous traits, low structural flower complexity and fast life
cycle. For the purpose of the experiment all the species where
considered as pollen recipient and as pollen donor (see interaction
matrix, fig 2). Species were watered once or twice per day and
fertilized weekly (NPK 23: 3.95: 14).

@@

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in table 2. Heterospecific pollen
reduced seet set signifcatively with the 50-50\% heterospecific pollen
treatments for 65\% of the pairwise interactions p\textless{}0.05.
Across families we found a very similar effect but when species where
look at species level they respond differently even within the same
family, for instance for two species of the Brassicaceae family
\emph{Brassica oleracea} and \emph{Eruca versicaria} we found very
contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did out of nine. The 100\% foreign pollen treatments barely
produced seeds or fruits and just for \emph{Sinapis alba} we did not
find significant differences between the hand cross pollination and one
treatment with pollen from a confamilial. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases.
\emph{S. lycopersicum} seems to produced small fruits (35\% of the
treatments) independently of pollen and pollen donor due to also
apomictic treatments did, never normal size. \emph{C. annum} produced
some fruits (9\%) of both small and normal size and finally \emph{S.
melongena} produced seedless normal fruits with just confamilial pollen
(3\%), for both species seems that fruit formation was induced by pollen
on the stigma because of no production of fruit in apomictic treatments.

>>>>

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The species selected
(\textbf{Table 1}) belonged to three different families, Solanaceae,
Brassicaceae and Convolvulaceae. The criteria of species/family
selection was based on close/distant related species (see phylogenetic
tree for relatedness fig 1), heterogeneous traits, low structural flower
complexity and fast life cycle. For the purpose of the experiment all
the species where considered as pollen recipient and as pollen donor
(see interaction matrix, fig 2). Species were watered once or twice per
day and fertilized weekly (NPK 23: 3.95: 14).

@@

Results of hand cross pollination, self hand pollination, natural
selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
pollen reduced seet set signifcatively with the 50-50\% heterospecific
pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
very contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did out of nine. The 100\% foreign pollen treatments barely
produced seeds or fruits and just for \emph{Sinapis alba} we did not
find significant differences between the hand cross pollination and one
treatment with pollen from a confamilial. Solanaceae species with berry
fruit type developed small fruits or even normal fruits in some cases.
\emph{S. lycopersicum} seems to produced small fruits (35\% of the
treatments) independently of pollen and pollen donor due to also
apomictic treatments did, never normal size. \emph{C. annum} produced
some fruits (9\%) of both small and normal size and finally \emph{S.
melongena} produced seedless normal fruits with just confamilial pollen
(3\%), for both species seems that fruit formation was induced by pollen
on the stigma because of no production of fruit in apomictic treatments.
